\textbf{ \Large{Decentralized autonomous sensor fault detection using neural networks}}

### 2015-02-03 Paper/PaperJahrSchlich.tex
Extended section 'laboratory experiments'

To validate the proposed approach, the SHM system is installed on a test structure in order to conduct laboratory experiments.
The test structure consists of four metal sheets with an area of 20\,cm by 60\,cm and 4\,mm of thickness.
Those metal sheets are mounted on threaded rods with a vertical clearance of approximately 40\,cm.
At the bottom, the threaded rods are fixed into a block of solid wood with an area of 40\,cm by 60\,cm and a height of 50\,cm.
The SHM system is installed onto the test structure by fastening a SunSPOT to each of the metal sheets.
The finished laboratory setup is shown in figure~\ref{fig:teststructure}.
\todo{Bild ersetzen durch ein Bild mit den fertig installierten SPOTS}
The structure is excited by displacing one of the metal sheets to the side and releasing it.
This method of excitation ensures, that the structure vibrates in its Eigenfrequency with little interferences.

@@

>>>>

To validate the proposed approach in laboratory experiments, the wireless SHM system is installed on a test structure.
The test structure is a 4-story shear-frame consisting of four steel plates with an area of 25\,cm\,$\times$\,50\,cm and a thickness of 0.8\,mm.
Those plates are mounted on threaded rods with a vertical clearance of 23\,cm.
At the bottom, the rods are fixed into a solid block of wood with an area of 40\,cm\,$\times$\,60\,cm and a height of 30\,cm.
The SHM system is installed on the test structure by fastening wireless sensor nodes to each story.
The laboratory setup is shown in figure~\ref{fig:teststructure}.
\todo{Bild ersetzen durch ein Bild mit den fertig installierten SPOTS}

@@

The structure is excited by deflecting and releasing the top of the structure.
This excitation method ensures that the structure vibrates in its Eigenfrequency with little interferences.
After excitation the sensor nodes automatically start measuring acceleration values with a sampling rate of 40\,Hz.
To minimize data traffic between the sensor nodes, each node performs a fast Fourier transform (FFT) algorithm after sufficient acceleration samples have been collected.
Generally FFTs are used to convert equidistant samples of a function into a combination of frequencies, and the corresponding magnitudes, that has the same sample values.
In this case the acceleration samples are converted into the vibration frequencies, and the corresponding magnitudes, of the building.
Each sensor node sends only the values of the predominating frequency, i.e. the frequency with the biggest magnitude, to the other nodes.
